Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-11 main_paper.tex
Tweak discussion of parts of assumption 1
This commit modifies the discussion of the different parts of Assumption 1 to be
more in line with my expectations of what the referee wants. It attributes the
parts to 'identification' or 'estimation' instead of simply restating the assumptions.

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and one limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model, however, the results and procedures can be
easily extended to the general local polynomial and higher order derivatives
cases (e.g., Regression Kink Designs, see \citealp{CardEtAl1,CardEtAl2}).

@@

In most cases, the population parameter of interest is the Average Treatment
Effect (ATE) at the cutoff, which we will denote $\tau$. This parameter is the
difference in expected potential outcomes given $X_i = 0$; formally,
\begin{equation*}
  \tau=\E(Y(1)-Y(0) \mid X=0)
\end{equation*}
with $\E$ representing the expectation.
\cite{HTV2001} show that the effect $\tau$ is identified under continuity and
smoothness conditions on the joint distribution of $X_i$, $Y_i(0)$, and $Y_i(1)$
around the cutoff $X_i = 0$. Under these conditions, which are made precise
in our Assumption~\ref{A1}, $\tau$ is equal to
\begin{equation*}
  \tau = \lim_{x \to 0+} \mu(x) - \lim_{x \to 0-} \mu(x)
\end{equation*}
where
\begin{equation*}
  \mu(x)= \E(Y_{i} \mid X_{i}=x).
\end{equation*}
For later convenience, also define the derivatives
\begin{equation*}
  \mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}
\end{equation*}
and let
\begin{align*}
  \mu_{+}(x)
  &= \E( Y_{i}(1) \mid X_{i}=x )
  &\mu_{-}(x)
  &= \E( Y_{i}(0) \mid X_{i}=x ) \\
  \sigma^{2}_{+}(x) &= \V( Y_{i}(1) \mid X_{i}=x )
  &\sigma^{2}_{-}(x)&=\V( Y_{i}(0) \mid X_{i}=x ) \\
\intertext{and}
  \mu^{(\eta)}_{+}
  &= \lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x),
  &\mu^{(\eta)}_{-}
  &= \lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x),
\end{align*}
where the symbol $\V(\cdot)$ represents the variance.  The effect $\tau$ is
nonparametrically identified because both $\mu_-$ and $\mu_+$ can be estimated
consistently under Assumption~\ref{A1}, which lists standard conditions in the
RD literature. (See, in particular, \citealp{HTV2001}, \citealp{Porter03}, and
CCT.)

@@

 The first part of Assumption \ref{A1} requires that the running variable be continuously distributed around the cutoff, and guarantees the presence of observations close to the threshold in large samples.
 Next, this assumption imposes the existence of moments necessary for estimation and inference.
 Part 3 imposes the traditional smoothness conditions on the expected potential outcomes and its derivatives around the cutoff which is crucial for identification of the parameters of interest and bias correction terms.
 Finally, the last part of Assumption \ref{A1} describes the standard restrictions on the conditional variance of the observed $Y_{i}$ around the cutoff, allowing for different values on each side of the threshold.

 Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}.} %

For this model, if $h$ represents a bandwidth parameter and $K(\cdot)$ a density
function, the estimator of $\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h}K(X_{i}/h)
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K(X_{i}/h).
\end{align*}

>>>>

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and one limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model, however, the results and procedures can be
easily extended to the general local polynomial and higher order derivatives
cases (e.g., Regression Kink Designs, see \citealp{card2009b}, and
\citealp{CardEtAl1,CardEtAl2}).

@@

In most cases, the population parameter of interest is the Average Treatment
Effect (ATE) at the cutoff, which we will denote $\tau$. This parameter is the
difference in expected potential outcomes given $X_i = 0$; formally,
\begin{equation*}
  \tau=\E(Y(1)-Y(0) \mid X=0)
\end{equation*}
with $\E$ representing the expectation.
\cite{HTV2001} show that the effect $\tau$ is identified under continuity and
smoothness conditions on the joint distribution of $X_i$, $Y_i(0)$, and $Y_i(1)$
around the cutoff $X_i = 0$. Under these conditions, which are made precise
in our Assumption~\ref{A1}, $\tau$ is equal to
\begin{equation*}
  \tau = \lim_{x \to 0+} \mu(x) - \lim_{x \to 0-} \mu(x)
\end{equation*}
where
\begin{equation*}
  \mu(x)= \E(Y_{i} \mid X_{i}=x).
\end{equation*}
For later convenience, also define the derivatives
\begin{equation*}
  \mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}
\end{equation*}
and let
\begin{align*}
  \mu_{+}(x)
  &= \E( Y_{i}(1) \mid X_{i}=x )
  &\mu_{-}(x)
  &= \E( Y_{i}(0) \mid X_{i}=x ) \\
  \sigma^{2}_{+}(x) &= \V( Y_{i}(1) \mid X_{i}=x )
  &\sigma^{2}_{-}(x)&=\V( Y_{i}(0) \mid X_{i}=x ) \\
\intertext{and}
  \mu^{(\eta)}_{+}
  &= \lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x),
  &\mu^{(\eta)}_{-}
  &= \lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x),
\end{align*}
where the symbol $\V(\cdot)$ represents the variance. Assumption~\ref{A1} lists
standard conditions in the RD literature which ensure that both $\mu_-$ and
$\mu_+$ can be estimated consistently.

@@

Part 1 and the continuity component of Part 3 of Assumption~\ref{A1} are crucial
for identifying $\tau$ --- informally, they ensure that the number of points
arbitrarily close to the cutoff increases with the sample size and that there is
a small neighborhood around the cutoff in which the change in the conditional
expectation can be attributed to the change in treatment status.  (See
\citealp{HTV2001}, and \citealp{Porter03}, for more detailed discussion of
identification in RD designs.) The additional smoothness conditions in Part 3
allow higher order polynomials to be used for estimation and Parts 2 and 4
ensure that the estimated local polynomials are well behaved.

Since these conditions only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, at the cost of stronger moment and smoothness assumptions.} %
For this model, if $h$ represents a bandwidth parameter and $K(\cdot)$ a density
function, the estimator of $\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h}K(X_{i}/h)
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K(X_{i}/h).
\end{align*}
